QPLIB: A Library of Quadratic Programming Instances

### 2017-01-23 methods.tex
add latex defines for solver names
- to make it easier to change their writing throughout the paper

Incomplete methods are usually realized as local search algorithms, asymptotically complete methods are usually realized by meta-heuristic methods such as multi-start or simulated annealing, and complete methods for $\mathcal{NP}$-hard problems such as QP are typically realized as implicit exhaustive exploration algorithms. However, these three categories may exhibit some overlap. For example, any deterministic method for solving QCQ locally is incomplete in general, but becomes complete for CCC, since any local optimum of a convex QP is also global. Therefore, when we state that a given algorithm is incomplete or (asymptotically) complete we mean that it is so the largest problem class that the solver naturally targets, although it may be complete on specific sub-classes. For example, {\sc SnOpt} naturally targets continuous NLPs and it is incomplete on nonconvex NLPs, and therefore on QCQ, but becomes complete for CCC. In general, all complete methods for a problem $P$ must be complete for any problem $Q \subseteq P$, while a complete method for $P$ might be incomplete for $R \supset P$.

@@

The solvers in Table \ref{t:solvers} which implement incomplete methods for continuous NLPs (a problem class containing QCQ) are {\sc ConOpt}, {\sc IpOpt}, {\sc Minos}, {\sc SnOpt} and {\sc KNitro}\todo{check capitalization of solver names}. The methods are local search algorithms and are essentially of the following types: %Note that traditionally {\sc KNitro} used to be a local (nonconvex) NLP solver.
%All of these solvers implement essentially three types of local search methods for continuous NLPs:
\todo{sequential linear programming, sequential quadratic programming, trust-region}
\begin{itemize}
 \item active set methods ({\sc ConOpt}, {\sc Minos}, {\sc SnOpt}, {\sc KNitro}) \cite{Dost09};
 %
 \item interior point methods ({\sc IpOpt}, {\sc KNitro}) \cite{Wright97};
 %
 \item projected gradient methods \cite{CalaMore87:mp,ChenGui13:coap}.
\end{itemize}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs. In fact, all of the solvers named above target this larger problem class.

@@

The solvers in Table \ref{t:solvers} which implement asymptotically complete methods are {\sc oqnlp}, {\sc msnlp}, {\sc knitro}, and certain sub-solvers of {\sc lgo}. Specifically, we consider the following methods:
%
\begin{itemize}
 \item global adaptive random search ({\sc lgo\_gars});
 %
 \item multi-start ({\sc knitro}, {\sc lgo\_ms}, {\sc msnlp}, {\sc oqnlp}); specifically, the former three apply to QCQ whereas the latter to QGQ.
\end{itemize}

\paragraph{Global Adaptive Random Search.}
%
This is a modification of an algorithm called {\it pure random search}, which consists in sampling a random point $x'$ from a given compact set known to contain a global optimum, and then sampling a new candidate solution $y$ in a neighborhood of $x'$, setting $x' \leftarrow y$ if $y$ improves $x'$, and repeating as long as a termination condition is not satisfied. The adaptivity stems from changing the distribution for sampling $y$ at run-time, depending on the quality of the solutions identified by the method. Since this method only depends on sampling and function evaluation, it is usually fast. In the {\sc lgo\_gars} solver, it provides a useful starting point for a subsequent local search procedure. Asymptotic global convergence is attained by restarting the random search from different initial points $x'$.

@@

The following solvers from Table \ref{t:solvers} implement complete BB algorithms for QGQ or some subclasses:
%
\begin{itemize}
 \item {\sc Antigone}, {\sc Baron}, {\sc Couenne}, {\sc Lindo API}, {\sc SCIP} for QGQ;
 %
\item {\sc CPLEX} for QGL and CGC;
%
 \item {\sc Knitro}, {\sc BonMin}, {\sc sBB}, {\sc Xpress}, {\sc Gurobi}, and {\sc Mosek} for CGC.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for QGQ. %We also remark that CPLEX can currently only target problems with linear constraints when the objective function is nonconvex \cite{bliek}.
We also remark that {\sc lgo} implements an incomplete BB algorithm for QCQ by using bounds obtained from sampling.

@@

Solvers in Table \ref{t:solvers} that implement complete cutting plane methods for CGC are {\sc AlphaECP} \cite{westerlund}, {\sc BonMin} (in the algorithmic mode B-OA) \cite{BBCCGLLLMSW} and {\sc DICOpt} \cite{quesada}. \todo{here we give references to the solvers, above we don't}

>>>>

Incomplete methods are usually realized as local search algorithms, asymptotically complete methods are usually realized by meta-heuristic methods such as multi-start or simulated annealing, and complete methods for $\mathcal{NP}$-hard problems such as QP are typically realized as implicit exhaustive exploration algorithms. However, these three categories may exhibit some overlap. For example, any deterministic method for solving QCQ locally is incomplete in general, but becomes complete for CCC, since any local optimum of a convex QP is also global. Therefore, when we state that a given algorithm is incomplete or (asymptotically) complete we mean that it is so the largest problem class that the solver naturally targets, although it may be complete on specific sub-classes. For example, \snopt naturally targets continuous NLPs and it is incomplete on nonconvex NLPs, and therefore on QCQ, but becomes complete for CCC. In general, all complete methods for a problem $P$ must be complete for any problem $Q \subseteq P$, while a complete method for $P$ might be incomplete for $R \supset P$.

@@

The solvers in Table \ref{t:solvers} which implement incomplete methods for continuous NLPs (a problem class containing QCQ) are \conopt, \ipopt, \minos, \snopt, and \knitro. The methods are local search algorithms and are essentially of the following types: %Note that traditionally \knitro used to be a local (nonconvex) NLP solver.
%All of these solvers implement essentially three types of local search methods for continuous NLPs:
\todo{sequential linear programming, sequential quadratic programming, trust-region}
\begin{itemize}
 \item active set methods (\conopt, \minos, \snopt, \knitro) \cite{Dost09};
 %
 \item interior point methods (\ipopt, \knitro) \cite{Wright97};
 %
 \item projected gradient methods \cite{CalaMore87:mp,ChenGui13:coap}.
\end{itemize}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs. In fact, all of the solvers named above target this larger problem class.

@@

The solvers in Table \ref{t:solvers} which implement asymptotically complete methods are \oqnlp, \msnlp, \knitro, and certain sub-solvers of \lgo. Specifically, we consider the following methods:
%
\begin{itemize}
 \item global adaptive random search (\lgo GARS);
 %
 \item multi-start (\knitro, \lgo MS, \msnlp, \oqnlp); specifically, the former three apply to QCQ whereas the latter to QGQ.
\end{itemize}

\paragraph{Global Adaptive Random Search (GARS).}
%
This is a modification of an algorithm called {\it pure random search}, which consists in sampling a random point $x'$ from a given compact set known to contain a global optimum, and then sampling a new candidate solution $y$ in a neighborhood of $x'$, setting $x' \leftarrow y$ if $y$ improves $x'$, and repeating as long as a termination condition is not satisfied. The adaptivity stems from changing the distribution for sampling $y$ at run-time, depending on the quality of the solutions identified by the method. Since this method only depends on sampling and function evaluation, it is usually fast. In the GARS solver of \lgo, it provides a useful starting point for a subsequent local search procedure. Asymptotic global convergence is attained by restarting the random search from different initial points $x'$.

@@

The following solvers from Table \ref{t:solvers} implement complete BB algorithms for QGQ or some subclasses:
%
\begin{itemize}
 \item \antigone, \baron, \couenne, \lindo, \scip for QGQ;
 %
\item \cplex for QGL and CGC;
%
 \item \knitro, \bonmin, \sbb, \xpress, \gurobi, and \mosek for CGC.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for QGQ. %We also remark that CPLEX can currently only target problems with linear constraints when the objective function is nonconvex \cite{bliek}.
We also remark that \lgo implements an incomplete BB algorithm for QCQ by using bounds obtained from sampling.

@@

Solvers in Table \ref{t:solvers} that implement complete cutting plane methods for CGC are \alphaecp \cite{westerlund}, \bonmin (in the algorithmic mode B-OA) \cite{BBCCGLLLMSW} and \dicopt \cite{quesada}. \todo{here we give references to the solvers, above we don't}

### 2017-01-23 solvers.tex
add latex defines for solver names
- to make it easier to change their writing throughout the paper

\begin{tabular}{lccccccc}
\toprule  
                 & CGL & QGL & CGC & QGQ & CCC & QCQ \\
\hline
{\sc AlphaECP}    &  C  &  I  &  C  &  I  &  C  &  I  \\
{\sc Antigone}    &  C  &  C  &  C  &  C  &  C  &  C  \\
{\sc Baron}       &  C  &  C  &  C  &  C  &  C  &  C  \\
{\sc BonMin}      &  C  &  I  &  C  &  I  &  C  &  I  \\
{\sc ConOpt}      &     &     &     &     &  C  &  I  \\
{\sc Couenne}     &  C  &  C  &  C  &  C  &  C  &  C  \\
{\sc CPLEX}       &  C  &  C  &  C  &     &  C  &     \\
{\sc DICOpt}      &  C  &  I  &  C  &  I  &  C  &  I  \\
{\sc FICO XPress} &  C  &     &  C  &     &  C  &     \\
{\sc Gurobi}      &  C  &     &  C  &     &  C  &     \\
{\sc IpOpt}       &     &     &     &     &  C  &  I  \\
{\sc KNitro}      &  C  &  I  &  C  &  I  &  C  &  A  \\
{\sc lindo api}   &  C  &  C  &  C  &  C  &  C  &  C  \\
{\sc lgo}         &     &     &     &     &  A  &  A  \\
{\sc Minos}       &     &     &     &     &  C  &  I  \\
{\sc mosek}       &  C  &     &  C  &     &  C  &     \\
{\sc msnlp}       &     &     &     &     &  C  &  A  \\
{\sc oqnlp}       &  A  &  A  &  A  &  A  &  C  &  A  \\
{\sc sBB}         &  C  &  I  &  C  &  I  &  C  &  I  \\
{\sc SCIP}        &  C  &  C  &  C  &  C  &  C  &  C  \\
{\sc SnOpt}       &     &     &     &     &  C  &  I  \\
\hline
\end{tabular}                 
\caption{Families of QP problems that can be tackled by each solver} \label{t:solvers}
}

\todo[inline]{Xpress has a solver for convex MIQCPs called Xpress-SLP.
However, it is not available within GAMS.
Should Table 2 take Xpress-SLP into account?}

>>>>

\begin{tabular}{lccccccc}
\toprule  
             & CGL & QGL & CGC & QGQ & CCC & QCQ \\
\hline
\alphaecp    &  C  &  I  &  C  &  I  &  C  &  I  \\
\antigone    &  C  &  C  &  C  &  C  &  C  &  C  \\
\baron       &  C  &  C  &  C  &  C  &  C  &  C  \\
\bonmin      &  C  &  I  &  C  &  I  &  C  &  I  \\
\conopt      &     &     &     &     &  C  &  I  \\
\couenne     &  C  &  C  &  C  &  C  &  C  &  C  \\
\cplex       &  C  &  C  &  C  &     &  C  &     \\
\dicopt      &  C  &  I  &  C  &  I  &  C  &  I  \\
\gurobi      &  C  &     &  C  &     &  C  &     \\
\ipopt       &     &     &     &     &  C  &  I  \\
\knitro      &  C  &  I  &  C  &  I  &  C  &  A  \\
\lindo       &  C  &  C  &  C  &  C  &  C  &  C  \\
\lgo         &     &     &     &     &  A  &  A  \\
\minos       &     &     &     &     &  C  &  I  \\
\mosek       &  C  &     &  C  &     &  C  &     \\
\msnlp       &     &     &     &     &  C  &  A  \\
\oqnlp       &  A  &  A  &  A  &  A  &  C  &  A  \\
\sbb         &  C  &  I  &  C  &  I  &  C  &  I  \\
\scip        &  C  &  C  &  C  &  C  &  C  &  C  \\
\snopt       &     &     &     &     &  C  &  I  \\
\xpress      &  C  &     &  C  &     &  C  &     \\
\hline
\end{tabular}                 
\caption{Families of QP problems that can be tackled by each solver} \label{t:solvers}
}
